---
title: "StasticalP1"
author: "Ayush Kumar"
date: "20/10/2020"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
```

```{r LoadingData, include=FALSE}
library(data.table)
library(ggplot2)
library(knitr)
opts_chunk$set(echo = TRUE, results = 'hold')
```

##Assigning Values

```{r Values}
set.seed(120)
expnum <- 40 
lambda <- 0.2 
simnum <- 1000
expsimu <- replicate(simnum, rexp(expnum, lambda)) 
expmean <- apply(expsimu, 2, mean)
```


##Q1 Show the sample mean and compare it to the theoretical mean of the distribution.

```{r}
analytic_mean<-mean(expmean)
analytic_mean

```

```{r}
theoretical_mean<-1/lambda
theoretical_mean
```

```{r}
analytic_mean-theoretical_mean
```

```{r}
hist(expmean, xlab = "mean", main = "Exponential Function Simulations")
abline(v = analytic_mean, col = "green")
abline(v = theoretical_mean, col = "yellow")

```

The analytics mean is 4.993867 wheras the theoretical mean is 5 showing that average centre of distribution is very close to theoretical centre of distribution.


##Q2 Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.

```{r}
theoreticl_variance<-(theoretical_mean)^2/expnum
theoreticl_variance
```

```{r}
sqrt_expnum<-sqrt(expnum)
theoretical_sd<-theoretical_mean/sqrt_expnum
theoretical_sd

```

```{r}
sampleVariance<- var(analytic_mean)
sampleVariance
```

```{r}
standard_deviation<-sd(expmean)
standard_deviation
```

```{r}
variance_distribution<-standard_deviation^2
variance_distribution
```

We could see that variance_distribution is same as sample_variance.

Theoretical Standard Deviation is 0.7905694.
Standard Deviation is 0.7865754.

##Q3 Show that the distribution is approximately normal.

```{r}
hist(expmean,  xlab="Mean for each trial", ylab = "Density", main="Sample Means Distribution", breaks=expnum, prob=TRUE)
lines(density(expmean))
abline(v = 1/lambda, col = "blue")
```


```{r}
qqnorm(expmean)
qqline(expmean, col = 2)
```

The above graph show a curve like structure(bell curve) and hence we could say that the distribution of 40 averages exponential is close to normal distribution.