---
title: "Part 2"
author: "Ayush Kumar"
date: "20/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Basic Inferential Data Analysis-We are going to analyze the ToothGrowth data in the R datasets package.

##Q1 Load the ToothGrowth data and perform some basic exploratory data analyses

```{r}
library(ggplot2)
data(ToothGrowth)
str(ToothGrowth)
head(ToothGrowth)
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
str(ToothGrowth)
qplot(dose, len, data=ToothGrowth, facets=.~supp, geom=c("point", "smooth"), method="loess")
```


##Q2 Provide a basic summary of the data.
```{r}
summary(ToothGrowth)
ggplot(aes(x=dose, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=dose))
ggplot(aes(x=supp, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=supp))

```


##Q3 Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.

```{r setup, include=FALSE}
varsupp <- ToothGrowth$supp
vardose <- ToothGrowth$dose
varlen <-  ToothGrowth$len
```

```{r setup, include=FALSE}
t.test(varlen[varsupp == "VC"],varlen[varsupp == "OJ"], paired=FALSE)
t.test(varlen[vardose == 0.5],varlen[vardose == 1], paired=FALSE)
```

##Q4 State your conclusions and the assumptions needed for your conclusions.


Conclusion-

1. For guiena pigs Vitamin c is a factor of growth for their teeth.
2. Whereas the delivery mode does not have any imapact on their growth.

Assumption-

1.We assume that variance in all groups should be expected to be equal.
2.The underlying assumption is that sampling of Guinea Pigs to assign them to a supplement and a dose was done properly.

